# (PART) Descriptive Statistics {-}

# Case Study


```{r message=FALSE, warning=FALSE, include=FALSE}
source("_common.R")
library(tidyverse)
```

## HERS-EA Survey Data

### Variables studied
```{r message=FALSE, warning=FALSE}
mksurvey <- as.data.frame(read_csv("_data/surveyresults.csv", col_names = TRUE, skip = 1))
names(mksurvey)

rownames(mksurvey) <- mksurvey[, 1]
mksurvey$Sex <- as.character(mksurvey$Sex)

IDs <- mksurvey[, 1:4]
respondentID <- mksurvey[, c(1,2,4)]
saveRDS(respondentID,"_data/respondentID.rds")

respondentNAMES <- mksurvey[, c(1, 3)]
saveRDS(respondentNAMES,"_data/respondentNAMES.rds")

saveRDS(mksurvey, "_data/mksurvey.rds")

```

<br>

### Variables selected for 5DE
> These variables can be modified by investigators to fit their research purpose.

```{r message=FALSE, warning=FALSE}
## Generate MK Table3 Data
library(readr)
library(dplyr)

mksurvey <- readRDS("_data/mksurvey.rds")

mktable3stats <- mksurvey %>% select(1:4, OwnItemAtHome, Chicken, Cattle, Goats, Pigs, Chicken_, Cattle_, Goats_, Pigs_, ItemFullOwnership, OwnLand, LandSize, AssetsOnLand, EarnIncome, WorkYouDo, WhoBuyItems, AllowedToSell, MoneySpendDecisions, AllowedTalkInPublic, TalkedInPublic, LeadershipPosition, SocialGroup, SourcesOfInfo, WorkYouDo, WorkingTime, HowOftenInLeisure)

mktable3stats <- mksurvey %>% select(1:4, OwnItemAtHome, Chicken, Cattle, Goats, Pigs, Chicken_, Cattle_, Goats_, Pigs_, ItemFullOwnership, OwnLand, LandSize, AssetsOnLand, EarnIncome, WorkYouDo, WhoBuyItems, AllowedToSell, MoneySpendDecisions, AllowedTalkInPublic, TalkedInPublic, LeadershipPosition, SocialGroup, SourcesOfInfo, WorkYouDo, WorkingTime, HowOftenInLeisure)

correctnames <- mksurvey %>% select(1:4, OwnItemAtHome, Chicken, Cattle, Goats, Pigs, ItemFullOwnership, OwnLand, LandSize, AssetsOnLand, EarnIncome, WorkYouDo, WhoBuyItems, AllowedToSell, MoneySpendDecisions, AllowedTalkInPublic, TalkedInPublic, LeadershipPosition, SocialGroup, SourcesOfInfo, WorkYouDo, WorkingTime, HowOftenInLeisure)
names(correctnames)

saveRDS(mktable3stats, "_data/mktable3stats.rds")
```

<br>

```{r}
### Load Table 3
mktable3stats <- readRDS("_data/mktable3stats.rds")

mktable3stats$RespondentID <- as.character(mktable3stats$RespondentID) 
mktable3stats$Phase <- as.character(mktable3stats$Phase) 
mktable3stats$Name <- as.character(mktable3stats$Name) 
mktable3stats$Sex <- as.character(mktable3stats$Sex) 
mktable3stats$OwnItemAtHome <- as.character(mktable3stats$OwnItemAtHome) 
mktable3stats$Chicken <- as.numeric(mktable3stats$Chicken) 
mktable3stats$Cattle <- as.numeric(mktable3stats$Cattle) 
mktable3stats$Goats <- as.numeric(mktable3stats$Goats) 
mktable3stats$Pigs <- as.numeric(mktable3stats$Pigs)
mktable3stats$Chicken_ <- as.character(mktable3stats$Chicken_) 
mktable3stats$Cattle_ <- as.character(mktable3stats$Cattle_) 
mktable3stats$Goats_ <- as.character(mktable3stats$Goats_) 
mktable3stats$Pigs_ <- as.character(mktable3stats$Pigs_) 
mktable3stats$ItemFullOwnership <- as.character(mktable3stats$ItemFullOwnership) 
mktable3stats$OwnLand <- as.character(mktable3stats$OwnLand) 
mktable3stats$LandSize <- as.character(mktable3stats$LandSize) 
mktable3stats$AssetsOnLand <- as.character(mktable3stats$AssetsOnLand) 
mktable3stats$EarnIncome <- as.character(mktable3stats$EarnIncome) 
mktable3stats$WorkYouDo <- as.character(mktable3stats$WorkYouDo) 
mktable3stats$WhoBuyItems <- as.character(mktable3stats$WhoBuyItems) 
mktable3stats$AllowedToSell <- as.character(mktable3stats$AllowedToSell) 
mktable3stats$MoneySpendDecisions <- as.character(mktable3stats$MoneySpendDecisions) 
mktable3stats$AllowedTalkInPublic <- as.character(mktable3stats$AllowedTalkInPublic) 
mktable3stats$TalkedInPublic <- as.character(mktable3stats$TalkedInPublic) 
mktable3stats$LeadershipPosition <- as.character(mktable3stats$LeadershipPosition) 
mktable3stats$SocialGroup <- as.character(mktable3stats$SocialGroup) 
mktable3stats$SourcesOfInfo <- as.character(mktable3stats$SourcesOfInfo) 
mktable3stats$WorkYouDo <- as.character(mktable3stats$WorkYouDo) 
mktable3stats$WorkingTime <- as.character(mktable3stats$WorkingTime) 
mktable3stats$HowOftenInLeisure <- as.character(mktable3stats$HowOftenInLeisure)

mktable3statsP1 <- mktable3stats %>% filter(Phase == "P1")
mktable3statsP2 <- mktable3stats %>% filter(Phase == "P2")

```

<br>
<hr>

# Numerical Variables
> Note that only the production domain has numerical variables that reflect the number of animals kept. It is also worth noting that WEAI is commonly constructed from categorical data.


## Descriptive Statistics {#numericalvarsstats}
Histogram of animals kept
```{r include=FALSE}
phase1 <- plot_num(mktable3statsP1)
phase2 <- plot_num(mktable3statsP2)
```

```{r fig.height=6, fig.width=10}
cowplot::plot_grid(phase1, phase2)
```

<br>

### Distribution of animals kept
```{r echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}
library(funModeling)
library(tidyr)
library(ggpubr)

prod4box <- mktable3stats %>% gather(key = Animal, value = value, Chicken, Cattle, Goats, Pigs, -Phase)

p1 <- prod4box %>% 
  ggplot(aes(x = Phase, y = value, fill = Animal)) +
  geom_boxplot() + theme_bw() + combosize

p2 <- prod4box %>% 
  ggplot(aes(x = Phase, y = log(value), fill = Animal)) +
  geom_boxplot() + theme_bw() + combosize

ggarrange(p1, p2, ncol = 1, common.legend = TRUE, legend = "right")
```

<br>
<hr>


**Chicken  Summary Stats**
```{r}
chickenP1 <- mktable3stats %>% select(RespondentID, Phase, Chicken) %>% filter(Phase == "P1")
names(chickenP1) <- c("RespondentID_P1", "Phase_P1", "Chicken_P1") 
chickenP2 <- mktable3stats %>% select(RespondentID, Phase, Chicken) %>% filter(Phase == "P2")
names(chickenP2) <- c("RespondentID_P2", "Phase_P2", "Chicken_P2") 
chickenProd <- data.frame(chickenP1, chickenP2)

summary(chickenProd)
```

Chicken Paired Sample T Test
```{r}
t.test(chickenProd$Chicken_P1, chickenP2$Chicken_P2)
```


**Cattle  Summary Stats**
```{r}
library(funModeling)
library(data.table)

cattleP1 <- mktable3stats %>% select(RespondentID, Phase, Cattle) %>% filter(Phase == "P1")
names(cattleP1) <- c("RespondentID_P1", "Phase_P1", "cattle_P1") 
cattleP2 <- mktable3stats %>% select(RespondentID, Phase, Cattle) %>% filter(Phase == "P2")
names(cattleP2) <- c("RespondentID_P2", "Phase_P2", "cattle_P2") 
cattleProd <- data.frame(cattleP1, cattleP2)

summary(cattleProd)

```

Cattle Paired Sample T Test
```{r}
t.test(cattleProd$cattle_P1, cattleP2$cattle_P2)
```

**Goats  Summary Stats**
```{r}
library(dplyr)
library(data.table)

goatsP1 <- mktable3stats %>% select(RespondentID, Phase, Goats) %>% filter(Phase == "P1")
names(goatsP1) <- c("RespondentID_P1", "Phase_P1", "Goats_P1") 
goatsP2 <- mktable3stats %>% select(RespondentID, Phase, Goats) %>% filter(Phase == "P2")
names(goatsP2) <- c("RespondentID_P2", "Phase_P2", "Goats_P2") 
goatsProd <- data.frame(goatsP1, goatsP2)

summary(goatsProd)
```

Goats Paired Sample T Test
```{r}
t.test(goatsProd$Goats_P1, goatsProd$Goats_P2)
```


**Pigs  Summary Stats**
```{r}
library(dplyr)
library(data.table)

pigP1 <- mktable3stats %>% select(RespondentID, Phase, Pigs) %>% filter(Phase == "P1")
names(pigP1) <- c("RespondentID_P1", "Phase_P1", "Pigs_P1") 
pigP2 <- mktable3stats %>% select(RespondentID, Phase, Pigs) %>% filter(Phase == "P2")
names(pigP2) <- c("RespondentID_P2", "Phase_P2", "Pigs_P2") 
pigProd <- data.frame(pigP1, pigP2)

summary(pigProd)

```

Pigs Paired Sample T Test
```{r}
t.test(pigProd$Pigs_P1, pigProd$Pigs_P2)
```

<br>
<hr>

# Categorical variables

## Descriptive Statistics {#categoricalvarsstats}
### Production Domain

#### Chicken


```{r}
chickP1 <- freq(mktable3statsP1, input = "Chicken_", plot = FALSE, na.rm = FALSE)
names(chickP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

chickP2 <- freq(mktable3statsP2, input = "Chicken_", plot = FALSE, na.rm = FALSE)
names(chickP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(chickP1, chickP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
Chicken <- c("Yes", "Unknown")

chickenDF <- data.frame(Chicken, Phase1, Phase2, Pvalue)

kable(chickenDF)
```

#### Cattle


```{r}
cattleP1 <- freq(mktable3statsP1, input = "Cattle_", plot = FALSE, na.rm = FALSE)
names(cattleP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

cattleP2 <- freq(mktable3statsP2, input = "Cattle_", plot = FALSE, na.rm = FALSE)
names(cattleP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(cattleP1, cattleP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
Cattle <- c("Yes", "Unknown")

cattleDF <- data.frame(Cattle, Phase1, Phase2, Pvalue)

kable(cattleDF)
```


#### Goats


```{r}
goatsP1 <- freq(mktable3statsP1, input = "Goats_", plot = FALSE, na.rm = FALSE)
names(goatsP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

goatsP2 <- freq(mktable3statsP2, input = "Goats_", plot = FALSE, na.rm = FALSE)
names(goatsP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(goatsP1, goatsP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
Goats <- c("Yes", "Unknown")

goatsDF <- data.frame(Goats, Phase1, Phase2, Pvalue)

kable(goatsDF)
```


#### Pigs


```{r}
pigsP1 <- freq(mktable3statsP1, input = "Pigs_", plot = FALSE, na.rm = FALSE)
names(pigsP1)[2:4] <- c("P1", "percentageP1","cumulative_percP1")

pigsP2 <- freq(mktable3statsP2, input = "Pigs_", plot = FALSE, na.rm = FALSE)
names(pigsP2)[2:4] <- c("P2", "percentageP2","cumulative_percP2")
merged <- merge(pigsP1, pigsP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(P1, P2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
Pigs <- c("Yes", "Unknown")

pigsDF <- data.frame(Pigs, Phase1, Phase2, Pvalue)

kable(pigsDF)
```


<br>
<hr>

### Resources Domain

#### Own land


```{r}
landP1 <- freq(mktable3statsP1, input = "OwnLand", plot = FALSE, na.rm = FALSE)
names(landP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

landP2 <- freq(mktable3statsP2, input = "OwnLand", plot = FALSE, na.rm = FALSE)
names(landP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(landP1, landP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "No", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
OwnLand <- c("Yes", "No", "Unknown")

ownlandDF <- data.frame(OwnLand, Phase1, Phase2, Pvalue)

kable(ownlandDF)
```


<br>


#### Land size


```{r}
sizeP1 <- freq(mktable3statsP1, input = "LandSize", plot = FALSE, na.rm = FALSE)
names(sizeP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

sizeP2 <- freq(mktable3statsP2, input = "LandSize", plot = FALSE, na.rm = FALSE)
names(sizeP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(sizeP1, sizeP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("≤1 acre", "2-5 acres", "Unknown", "5-10 acres", ">10 acres"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
LandSize <-c("≤1 acre", "2-5 acres", "Unknown", "5-10 acres", ">10 acres")

landsizeDF <- data.frame(LandSize, Phase1, Phase2, Pvalue)

kable(landsizeDF)
```

#### Assets on land


```{r}
assetsP1 <- freq(mktable3statsP1, input = "AssetsOnLand", plot = FALSE, na.rm = FALSE)
names(assetsP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

assetsP2 <- freq(mktable3statsP2, input = "AssetsOnLand", plot = FALSE, na.rm = FALSE)
names(assetsP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(assetsP1, assetsP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Perrenial Crops", "Animals", "Unknown", "Trees"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
AssetsOnLand <- c("Perrenial Crops", "Animals", "Unknown", "Trees")

assetsDF <- data.frame(AssetsOnLand, Phase1, Phase2, Pvalue)

kable(assetsDF)
```

<br>
<hr>

### Income Domain

#### Earn Income


```{r}
earnincomeP1 <- freq(mktable3statsP1, input = "EarnIncome", plot = FALSE, na.rm = FALSE)
names(earnincomeP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

earnincomeP2 <- freq(mktable3statsP2, input = "EarnIncome", plot = FALSE, na.rm = FALSE)
names(earnincomeP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(earnincomeP1, earnincomeP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown", "No"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
EarnIncome <-  c("Yes", "Unknown", "No")

earnincomeDF <- data.frame(EarnIncome, Phase1, Phase2, Pvalue)

kable(earnincomeDF)
```



#### Source of Income


```{r}
workyoudoP1 <- freq(mktable3statsP1, input = "WorkYouDo", plot = FALSE, na.rm = FALSE)
names(workyoudoP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

workyoudoP2 <- freq(mktable3statsP2, input = "WorkYouDo", plot = FALSE, na.rm = FALSE)
names(workyoudoP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(workyoudoP1, workyoudoP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Sell produce", "Home-based Business", "Unknown", "Homework", "Salary"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
WorkYouDo <-  c("Sell produce", "Home-based Business", "Unknown", "Homework", "Salary")

workyoudoDF <- data.frame(WorkYouDo, Phase1, Phase2, Pvalue)

kable(workyoudoDF)
```


#### Who buys items at home


```{r}
whobuyP1 <- freq(mktable3statsP1, input = "WhoBuyItems", plot = FALSE, na.rm = FALSE)
names(whobuyP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

whobuyP2 <- freq(mktable3statsP2, input = "WhoBuyItems", plot = FALSE, na.rm = FALSE)
names(whobuyP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(whobuyP1, whobuyP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Me",  "My spouse", "Unknown", "Both on Consultation", "Other (sponsor, children, etc."), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
WhoBuyItems <-  c("Me",  "My spouse", "Unknown", "Both on Consultation", "Other (sponsor, children, etc.")

whobuyDF <- data.frame(WhoBuyItems, Phase1, Phase2, Pvalue)

kable(whobuyDF)
```



#### Allowed to sell or buy


```{r}
allowedtobuyP1 <- freq(mktable3statsP1, input = "AllowedToSell", plot = FALSE, na.rm = FALSE)
names(allowedtobuyP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

allowedtobuyP2 <- freq(mktable3statsP2, input = "AllowedToSell", plot = FALSE, na.rm = FALSE)
names(allowedtobuyP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(allowedtobuyP1, allowedtobuyP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Me", "Both on Consultation",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
AllowedToBuyOrSell <-  c("Me", "Both on Consultation", "Unknown")

allowedtobuyDF <- data.frame(AllowedToBuyOrSell, Phase1, Phase2, Pvalue)

kable(allowedtobuyDF)
```


#### Who decides how to spend


```{r}
decidetospendP1 <- freq(mktable3statsP1, input = "MoneySpendDecisions", plot = FALSE, na.rm = FALSE)
names(decidetospendP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

decidetospendP2 <- freq(mktable3statsP2, input = "MoneySpendDecisions", plot = FALSE, na.rm = FALSE)
names(decidetospendP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(decidetospendP1, decidetospendP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Me", "Other",  "My spouse", "Unknown", "Both on Consultation"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
MoneySpendDecisions  <-  c("Me", "Other",  "My spouse", "Unknown", "Both on Consultation")

decidetospendDF <- data.frame(MoneySpendDecisions, Phase1, Phase2, Pvalue)

kable(decidetospendDF)
```


### Leadership

#### Allowed to speak in public

```{r}
allowedtospeakinpublicP1 <- freq(mktable3statsP1, input = "AllowedTalkInPublic", plot = FALSE, na.rm = FALSE)
names(allowedtospeakinpublicP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

allowedtospeakinpublicP2 <- freq(mktable3statsP2, input = "AllowedTalkInPublic", plot = FALSE, na.rm = FALSE)
names(allowedtospeakinpublicP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(allowedtospeakinpublicP1, allowedtospeakinpublicP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "Unknown",  "No"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
AllowedTalkInPublic  <-  c("Yes", "Unknown",  "No")

allowedtospeakinpublicDF <- data.frame(AllowedTalkInPublic, Phase1, Phase2, Pvalue)

kable(allowedtospeakinpublicDF)
```

#### Everspoken in public

```{r}
everspokeninpublicP1 <- freq(mktable3statsP1, input = "TalkedInPublic", plot = FALSE, na.rm = FALSE)
names(everspokeninpublicP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

everspokeninpublicP2 <- freq(mktable3statsP2, input = "TalkedInPublic", plot = FALSE, na.rm = FALSE)
names(everspokeninpublicP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(everspokeninpublicP1, everspokeninpublicP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "No",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
TalkedInPublic  <-  c("Yes", "No",  "Unknown")

everspokeninpublicDF <- data.frame(TalkedInPublic, Phase1, Phase2, Pvalue)

kable(everspokeninpublicDF)
```

#### Held Leadership position

```{r}
leadershippositionP1 <- freq(mktable3statsP1, input = "LeadershipPosition", plot = FALSE, na.rm = FALSE)
names(leadershippositionP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

leadershippositionP2 <- freq(mktable3statsP2, input = "LeadershipPosition", plot = FALSE, na.rm = FALSE)
names(leadershippositionP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(leadershippositionP1, leadershippositionP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "No",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
LeadershipPosition  <-  c("Yes", "No",  "Unknown")

leadershippositionDF <- data.frame(LeadershipPosition, Phase1, Phase2, Pvalue)

kable(leadershippositionDF)
```

#### Belong to social groups

```{r}
socialgroupP1 <- freq(mktable3statsP1, input = "SocialGroup", plot = FALSE, na.rm = FALSE)
names(socialgroupP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

socialgroupP2 <- freq(mktable3statsP2, input = "SocialGroup", plot = FALSE, na.rm = FALSE)
names(socialgroupP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(socialgroupP1, socialgroupP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "No",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
SocialGroup  <-  c("Yes", "No",  "Unknown")

socialgroupDF <- data.frame(SocialGroup, Phase1, Phase2, Pvalue)

kable(socialgroupDF)
```

#### Sources of Information

```{r}
sourcesinfoP1 <- freq(mktable3statsP1, input = "SourcesOfInfo", plot = FALSE, na.rm = FALSE)
names(sourcesinfoP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

sourcesinfoP2 <- freq(mktable3statsP2, input = "SourcesOfInfo", plot = FALSE, na.rm = FALSE)
names(sourcesinfoP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(sourcesinfoP1, sourcesinfoP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("One", "Two",  ">Two",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
SourcesOfInfo  <-  c("One", "Two",  ">Two",  "Unknown")

sourcesinfoDF <- data.frame(SourcesOfInfo, Phase1, Phase2, Pvalue)

kable(sourcesinfoDF)
```















### Time

#### Type of work or job

```{r}
workyoudoP1 <- freq(mktable3statsP1, input = "WorkYouDo", plot = FALSE, na.rm = FALSE)
names(workyoudoP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

workyoudoP2 <- freq(mktable3statsP2, input = "WorkYouDo", plot = FALSE, na.rm = FALSE)
names(workyoudoP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(workyoudoP1, workyoudoP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Homework", "Sell produce", "Home-based Business", "Salary", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
WorkYouDo <-  c("Homework", "Sell produce", "Home-based Business", "Salary", "Unknown")

workyoudoDF <- data.frame(WorkYouDo, Phase1, Phase2, Pvalue)

kable(workyoudoDF)
```


#### Working time
```{r}
workingtimeP1 <- freq(mktable3statsP1, input = "WorkingTime", plot = FALSE, na.rm = FALSE)
names(workingtimeP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

workingtimeP2 <- freq(mktable3statsP2, input = "WorkingTime", plot = FALSE, na.rm = FALSE)
names(workingtimeP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(workingtimeP1, workingtimeP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Morning to midday", "Morning to evening",  "Unknown", "Other"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
WorkingTime  <-  c("Morning to midday", "Morning to evening",  "Unknown", "Other")

workingtimeDF <- data.frame(WorkingTime, Phase1, Phase2, Pvalue)

kable(workingtimeDF)
```

#### Belong to social groups

```{r}
socialgroupP1 <- freq(mktable3statsP1, input = "SocialGroup", plot = FALSE, na.rm = FALSE)
names(socialgroupP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

socialgroupP2 <- freq(mktable3statsP2, input = "SocialGroup", plot = FALSE, na.rm = FALSE)
names(socialgroupP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(socialgroupP1, socialgroupP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("Yes", "No",  "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
SocialGroup  <-  c("Yes", "No",  "Unknown")

socialgroupDF <- data.frame(SocialGroup, Phase1, Phase2, Pvalue)

kable(socialgroupDF)
```

#### Leisure time

```{r}
leisureP1 <- mktable3statsP1 %>% select(RespondentID, Phase, Sex, HowOftenInLeisure)
leisureP1$HowOftenInLeisure[leisureP1$HowOftenInLeisure <=1] <- "≤ 1 hour/day" 
leisureP1$HowOftenInLeisure[leisureP1$HowOftenInLeisure ==2] <- "2 hours/day" 
leisureP1$HowOftenInLeisure[leisureP1$HowOftenInLeisure >=3] <- "≥ 3 hours/day" 
leisureP1$HowOftenInLeisure[leisureP1$HowOftenInLeisure >=3] <- "≥ 3 hours/day" 
leisureP1$HowOftenInLeisure[leisureP1$HowOftenInLeisure ==24] <- "≥ 3 hours/day" 

leisureP2 <- mktable3statsP2 %>% select(RespondentID, Phase, Sex, HowOftenInLeisure)
leisureP2$HowOftenInLeisure[leisureP2$HowOftenInLeisure <=1] <- "≤ 1 hour/day" 
leisureP2$HowOftenInLeisure[leisureP2$HowOftenInLeisure ==2] <- "2 hours/day" 
leisureP2$HowOftenInLeisure[leisureP2$HowOftenInLeisure >=3] <- "≥ 3 hours/day" 
leisureP2$HowOftenInLeisure[leisureP2$HowOftenInLeisure == 24] <- "≥ 3 hours/day" 

leisuretimeP1 <- freq(leisureP1, input = "HowOftenInLeisure", plot = FALSE, na.rm = FALSE)
names(leisuretimeP1)[2:4] <- c("frequencyP1", "percentageP1","cumulative_percP1")

leisuretimeP2 <- freq(leisureP2, input = "HowOftenInLeisure", plot = FALSE, na.rm = FALSE)
names(leisuretimeP2)[2:4] <- c("frequencyP2", "percentageP2","cumulative_percP2")
merged <- merge(leisuretimeP1, leisuretimeP2, all = TRUE, sort = FALSE)

# merged

```

<br> 

*Pearson's Chi-squared test*
```{r}
chisqset <- merged %>% select(frequencyP1, frequencyP2)
dimnames(chisqset) <- list(results = c("≥ 3 hours/day", "≤ 1 hour/day", "2 hours/day", "Unknown"), results = c("P1","P2"))

Phase1 = chisqset$P1
Phase2 = chisqset$P2
Pvalue = (chisq.test(chisqset))$p.value
HowOftenInLeisure  <-  c("≥ 3 hours/day", "≤ 1 hour/day", "2 hours/day", "Unknown")

leisuretimeDF <- data.frame(HowOftenInLeisure, Phase1, Phase2, Pvalue)

kable(leisuretimeDF)
```

<br>
<hr>

## Summary Statistics (MKTable3)
```{r message=FALSE, warning=FALSE}
library(readr)
mktable3stats4pub <- read_delim("_data/tmbtable3stats.csv", col_names = TRUE, delim = "\t", skip = 1)
mktable3stats4pub[is.na(mktable3stats4pub)] <- ""
mktable3stats4pub

write_csv(mktable3stats4pub, "_data/mktable3stats4pub.csv")
saveRDS(mktable3stats4pub, "_data/mktable3stats4pub.rds")
```
