
# Indicator Matrix


```{r message=FALSE, warning=FALSE, echo=FALSE}
source("_common.R")
nonzero <- function(x) sum(x != 0)

load("_data/packages.RData")
load("_data/globalSetup.RData")
mktable3stats <- readRDS("_data/mktable3stats.rds")

d01_poultry <- readRDS("_data/d1_poultry.rds")
d02_largeanimals <- readRDS("_data/d2_largeanimals.rds")
d03_ownassets <- readRDS("_data/d3_ownassets.rds")
d04_assetsonland <- readRDS("_data/d4_assetsonland.rds")
d05_earnincome <- readRDS("_data/d5_earnincome.rds")
d06_allowedtosell <- readRDS("_data/d6_allowedtosell.rds")
d07_speakinpublic <- readRDS("_data/d7_speakinpublic.rds")
d08_leadership <- readRDS("_data/d8_leadership.rds")
d09_workload <- readRDS("_data/d9_workload.rds")
d10_leisuretime <- readRDS("_data/d10_leisuretime.rds")
```


## Achievement Across Indicators

```{r}
indicatormatrix <- cbind(d01_poultry$d1, d02_largeanimals$d2, d03_ownassets$d3, d04_assetsonland$d4, d05_earnincome$d5, d06_allowedtosell$d6, d07_speakinpublic$d7, d08_leadership$d8, d09_workload$d9, d10_leisuretime$d10)
colnames(indicatormatrix) <- c("d01", "d02", "d03", "d04", "d05", "d06", "d07", "d08", "d09", "d10")
rownames(indicatormatrix) <- rownames(mktable3stats)

indicatormatrix <- as.data.frame(indicatormatrix)
cat("\n")
cat("Dimension of achievement matrix is", length(rownames(indicatormatrix)), "respondents and ", length(colnames(indicatormatrix)), "indicators (",length(rownames(indicatormatrix)), "x", length(colnames(indicatormatrix)),")")

cat("\n")
cat("Data Structure\n")
indicatormatrix

saveRDS(indicatormatrix, "_data/indicatormatrix.rds")

```

<br>

```{block, type="tmbinfo", echo=TRUE}
**Recall**: The indicator matrix is constructed by aggregating sub-indicator's achievements.

### Observation {-}
* Mattrix size is 158 x 10.
* May include nonresponses across all ten indicator in either survey phase.
* Next: We need to clean this data to retain the respondents who had at least one response in at least one indicator.
```

<br>

## Responses Matrix

```{r}
library(tidyverse)

indicatormatrix <- readRDS("_data/indicatormatrix.rds")
respondentID <- readRDS("_data/respondentID.rds")

# For the purposes of cleaning only
indicatormatrixwsum <- indicatormatrix
indicatormatrixwsum$Sum <- rowSums(indicatormatrix)
saveRDS(indicatormatrixwsum, "_data/indicatormatrixwsum.rds")

indicatormatrixwsumwvar <- cbind(respondentID, indicatormatrixwsum)
saveRDS(indicatormatrixwsumwvar, "_data/indicatormatrixwsumwvar.rds")

indicatormatrixwsumtidy <- indicatormatrixwsumwvar %>% filter(Sum > 0)
saveRDS(indicatormatrixwsumtidy, "_data/indicatormatrixwsumtidy.rds")

tidyID <- indicatormatrixwsumtidy[, c(1:3)]
saveRDS(tidyID, "_data/tidyID.rds")

cat("Total Responses =", length(indicatormatrixwsumtidy$RespondentID))
indicatormatrixtidy <- indicatormatrixwsumtidy[, -c(1:3, 14)]
indicatormatrixtidy

saveRDS(indicatormatrixtidy, "_data/indicatormatrixtidy.rds")

```

<br>

## Nonresponses Matrix
```{r}
indicatoruntidy <- indicatormatrixwsumwvar %>% filter(Sum == 0)

untidyID <- indicatoruntidy[, c(1:3)]
saveRDS(untidyID, "_data/untidyID.rds")

cat("Total Nonresponses =", length(indicatoruntidy$RespondentID))
indicatormatrixuntidy <- indicatoruntidy
indicatormatrixuntidy

saveRDS(indicatormatrixuntidy, "_data/indicatormatrixuntidy.rds")

```


<br>

## Response Proportion
```{r fig.height=6, fig.width=6, message=FALSE, warning=FALSE}

indicatormatrixwsumwvar <- readRDS("_data/indicatormatrixwsumwvar.rds")

respP1 <- indicatormatrixwsumwvar %>% filter(Phase == "P1", Sum > 0)
countrespP1 <- length(respP1$RespondentID)
nonrespP1 <- indicatormatrixwsumwvar %>% filter(Phase == "P1", Sum == 0)
countnonrespP1 <- length(nonrespP1$RespondentID)

respP2 <- indicatormatrixwsumwvar %>% filter(Phase == "P2", Sum > 0)
countrespP2 <- length(respP2$RespondentID)
nonrespP2 <- indicatormatrixwsumwvar %>% filter(Phase == "P2", Sum == 0)
countnonrespP2 <- length(nonrespP2$RespondentID)


dfP1 <- data.frame(
variable <- c("One or more Responses", "Nonresponse (to be removed)"),
value = c(countrespP1, countnonrespP1))

title1 <- paste("\nPhase One:", countrespP1, "Responses vs", countnonrespP1, "Nonresponses")
p1 <- dfP1 %>% 
ggplot(aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c("purple", "green")) +
  coord_polar("y", start = pi/10) +
  labs(title = title1, fill = "Response") + noxtitle + noxticks + noxlabels +  noytitle + noyticks + noylabels

dfP2 <- data.frame(
variable <- c("One or more Responses", "Nonresponse (to be removed)"),
value = c(countrespP2, countnonrespP2))


title2 <- paste("\nPhase Two:", countrespP2, "Responses vs", countnonrespP2, "Nonresponses")
p2 <- dfP2 %>% 
ggplot(aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c("purple", "green")) +
  coord_polar("y", start = pi/10) +
  labs(title = title2, fill = "Response") + noxtitle + noxticks + noxlabels +  noytitle + noyticks + noylabels

ggpubr::ggarrange(p1, p2, nrow = 2, ncol = 1)

```



<br>

## Individual's Adequacy
* This is an interactive heatmap, which shows the respondent's values for each indicator (d1 through d6).
* Mouseover to see the indicator, respondent ID, and a numerical value showing a sub-indicator count within the indicator.
* You can zoom, hover, pan, and even export a portion of the plot to your computer. 
* Note that the last column shows total individual achievement in all indicators.

```{r fig.height=15}
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(plotly)
library(d3heatmap)
library(reshape2)

indicatormatrixwsumtidy <- readRDS("_data/indicatormatrixwsumtidy.rds")

mat1 <- as.matrix(indicatormatrixwsumtidy[, -c(1:3)])
mat1.m <- melt(mat1)

colnames(mat1.m) <- c("RespondentID", "Indicator", "Value")

p1 <- ggplot(mat1.m, aes(x=Indicator, y=RespondentID, fill=Value)) + 
  geom_tile(mapping = NULL, data = NULL, stat = "identity",
  position = "identity", na.rm = TRUE,inherit.aes = TRUE) +
  labs(title = "", x="Indicator ID", y="Respondent ID", "Value") 

p1 <- p1 + scale_fill_viridis()

ggplotly(p1)
```






